---
title: "One-Way ANOVA"
subtitle: "Class Activity"
author: "Andrew Seaman"
date: "2025-Feb-10"
output: 
  html_document:
    theme: journal
    toc: true
    toc_float: true
    code_folding: hide
---

<!-- ------ -->
<!-- SETUP: -->
<!-- ------ -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
# Load libraries
library(mosaic)
library(DT)
library(pander)
library(tidyverse)
```

```{r}
# Import dataset
kf <- KidsFeet
```

<!-- Setup End -->










<!-- ---------- -->
<!-- QUESTIONS: -->
<!-- ---------- -->



<!-- Did this IN CLASS: -->


## Factor
**Definition:** A factor is defined as a qualitative variable containing at least two categories. The categories of the factor are referred to as the “levels” of the factor.

By using `as.factor(x)` on the categorical variable we can treat it as data type factor.

View the data types with either `str()`.`glimpse()`.
```{r}
# a. View the data types with `glimpse()`
glimpse(kf)
```

## ANOVA
**Notation:** `aov()`.

You have to run the analysis and assign it to a varaible first and then view the summary of that variable second.
```{r}
# a. 

# b.


# c.


# d.


```

<!-- In class End -->









## 1.
> _[Question]_

[Response]

```{r}
# a.


# b.


# c.


# d.


```

<!-- Q1. End -->










## 2.
> _[Question]_

[Response]

```{r}
# a.


# b.


# c.


# d.


```

<!-- Q2. End -->










## 3.
> _[Question]_

[Response]
```{r}
# a.


# b.


# c.


# d.


```

<!-- Q3. End -->










## 4.
> _[Question]_

[Response]
```{r}
# a.


# b.


# c.


# d.


```

<!-- Q4. End -->










## 5.
> _[Question]_

[Response]
```{r}
# a.


# b.


# c.


# d.


```

<!-- Q5. End -->










## 6.
> _[Question]_

[Response]
```{r}
# a.


# b.


# c.


# d.


```

<!-- Q6. End -->










## 7.
> _[Question]_

[Response]
```{r}
# a.


# b.


# c.


# d.


```

<!-- Q7. End -->










## 8.
> _[Question]_

[Response]
```{r}
# a.


# b.


# c.


# d.


```

<!-- Q8. End -->










## 9.
> _[Question]_

[Response]
```{r}
# a.


# b.


# c.


# d.


```

<!-- Q9. End -->










## 10.
> _[Question]_

[Response]
```{r}
# a.


# b.


# c.


# d.


```

<!-- Q10. End -->


<!-- Questions End -->




<!-- -------- -->
<!-- FILE END -->
<!-- -------- -->